Extending Camellia for Distributed Stiffness Matrix Determination in DPG

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added static condensation note at end
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@100 36274a68-8941-4c93-80ef-affaed5139da

Describe experimental setup
\begin{figure}
\centering
\subfigure[Cyclic]{
\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
}
\subfigure[HSFC]{
\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
}
\end{figure}

@@

\subsection{Breakdown of time spent}
\begin{figure}
\centering
\subfigure[202 elements, 13343 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref0.pdf}
}
\subfigure[808 elements, 52137 dofs ]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref1.pdf}
}
\subfigure[3232 elements, 206081 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref2.pdf}
}
\subfigure[12928 elements, 819393 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref3.pdf}
}
\caption{Strong scaling statistics for a cyclic (non-localized) partitioning of the mesh.}
\end{figure}

Handicaps
- Batch cache size 
- Using all 12 cores on a single node

@@

Another benefit of the hybridized DG formulation is that the global solve can be statically condensed down to a solve involving only the flux degrees of freedom.

>>>>

\begin{itemize}
\item Describe experimental setup

\item Handicaps - batch cache size, using all 12 cores on a single node

\item

\end{itemize}

\begin{figure}
\centering
\subfigure[Cyclic]{
\includegraphics[scale = \twoFig]{figs/cyclic.pdf}
}
\subfigure[HSFC]{
\includegraphics[scale = \twoFig]{figs/hsfc.pdf}
}
\end{figure}

@@

\subsection{Breakdown of time spent}

\begin{figure}
\centering
\subfigure[202 elements, 13343 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref0.pdf}
}
\subfigure[808 elements, 52137 dofs ]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref1.pdf}
}
\subfigure[3232 elements, 206081 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref2.pdf}
}
\subfigure[12928 elements, 819393 dofs]{
\includegraphics[scale = \fourFig]{figs/scalingFigs/bar_ref3.pdf}
}
\caption{Breakdown of time spent in a solve for a series of HSFC-partitioned meshes.}
\end{figure}

@@

Another benefit of the hybridized DG formulation is that the global solve can be reduced down to a solve involving only the flux degrees of freedom. Since the interior degrees of freedom are completely decoupled from each other, the system can be reordered to yield 
\[
\left(\begin{array}{cc}
A &B\\
B^T &C
\end{array}
\right)
\left(\begin{array}{c}
u\\
f
\end{array}
\right) = 
\left(\begin{array}{c}
F\\
G
\end{array}
\right)
\]
where $A$ is block diagonal. Noting that $u = A^{-1}(F-Bf)$, we can substitute this into the second solution to obtain a problem purely in terms of the flux degrees of freedom
\[
(C-B^TA^{-1}B)f = G-B^TA^{-1}F
\]
Since $A$ is easy to invert, and $B$ is a much smaller system, this \emph{static condensation} would reduce the cost of the solve.
